Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-27 main.Rmd
Expand into a paragraph - how does it illustrate the linear granularities? How does hour, day,... relate to G...}

\todo[inline]{Expand into a paragraph - how does it illustrate the linear granularities? How does hour, day,... relate to G...} <!--, each of which are non-repeating in nature and arranged from past to future. If we consider $T$ hours, we will have $\lfloor T/24\rfloor$ days, $\lfloor T/(24*7)\rfloor$ weeks and so on.-->

@@

\autoref{fig:circular-dow} \todo[inline]{C(B,G) should be above C(B,H) in figure, and yuo could add the integers to the stacked sets.} illustrates the linear and the corresponding cyclical granularities. Cyclical granularities can be considered to be cutting the linear granularity into pieces, and stacking them to match the cycles (as shown in b). $B, G, H$ (day, week, fortnight, respectively) are linear granularities. The circular granularity $C_{B , G}$ (day-of-week)is constructed from $B$ and  $G$. The circular granularity $C_{B, H}$ (day-of-fortnight) is constructed from $B$ and $H$. These overlapping cyclical granularities share elements from the linear granularity. Each of $C_{B , G}$ and $C_{B , H}$ consist of repeated patterns  $\{0, 1, 2, \dots, 6\}$ and $\{0, 1, 2, \dots, 13\}$ with $P=7$ and $P=14$ respectively.

>>>>

 <!--, each of which are non-repeating in nature and arranged from past to future. If we consider $T$ hours, we will have $\lfloor T/24\rfloor$ days, $\lfloor T/(24*7)\rfloor$ weeks and so on.-->

@@

\autoref{fig:circular-dow} illustrates the linear and the corresponding cyclical granularities. Cyclical granularities can be considered to be cutting the linear granularity into pieces, and stacking them to match the cycles (as shown in b). $B, G, H$ (day, week, fortnight, respectively) are linear granularities. The circular granularity $C_{B , G}$ (day-of-week)is constructed from $B$ and  $G$. The circular granularity $C_{B, H}$ (day-of-fortnight) is constructed from $B$ and $H$. These overlapping cyclical granularities share elements from the linear granularity. Each of $C_{B , G}$ and $C_{B , H}$ consist of repeated patterns  $\{0, 1, 2, \dots, 6\}$ and $\{0, 1, 2, \dots, 13\}$ with $P=7$ and $P=14$ respectively.
